Functional Enrichment Tests: Intro and methods comparison

### 2023-07-25 DRAFT_Funct_Enrich.Rmd
clean up api code

```{r setup, include=FALSE}
library(tidyverse)
library(reticulate)
```

@@

**Using API** (DOES NOTE WORK)

```{python}
#DRAFT_Funct_Enrich/annot/uniprot-retrieval.py DRAFT_Funct_Enrich/annot/SPID.txt
```

>>>>

```{r setup, include=FALSE}
library(tidyverse)
library(reticulate)

@@

**Using API**

```{r, include=FALSE}
knitr::opts_chunk$set(engine.path = '/usr/bin/python3')

```{python}
uniprot-retrieval.py SPID.txt
```

```{r, engine.path = '/usr/bin/python3'}
uniprot-retrieval.py
```
